---
title: "Legal Reasonableness - Analysis"
output: html_notebook
---
```{r}

# Load Libraries

library(dplyr)
library(purrr)
library(readxl)
library(stats)

```

# Analysis 1: Overall results, mean ratings [following Bear & Knobe 2016]

```{r}

## Step 1: Exclude participants whose answer to Q19 does not equal 15 [comprehension/attention question].

Data_All_Average_Pass1 <- Data_All_Average[Data_All_Average$q19 == 15, ]
Data_All_Ideal_Pass1 <- Data_All_Ideal[Data_All_Ideal$q19 == 15, ]
Data_All_Reasonable_Pass1 <- Data_All_Reasonable[Data_All_Reasonable$q19 == 15, ]

```
 
```{r}

## Step 2: For each of the 33 questions (e.g. Q1, Q2, but not Q19) and each of the 3 conditions (reasonable, average, or ideal), compute the mean rating. For any response that is greater than 3 standard deviations from that question mean, exclude that response.

### Make Column Numbers

question_cols <- paste0("q", c(1:18, 20:34)) # Make Column Numbers

### Make Sure All Data is Perceived as Numeric

Data_All_Average_Pass1[question_cols] <- lapply(Data_All_Average_Pass1[question_cols], as.numeric)

Data_All_Ideal_Pass1[question_cols] <- lapply(Data_All_Ideal_Pass1[question_cols], as.numeric)

Data_All_Reasonable_Pass1[question_cols] <- lapply(Data_All_Reasonable_Pass1[question_cols], as.numeric)


### Create a function to apply the exclusion criterion and calculate mean and standard deviation to each column
filter_data <- function(data) {
  #### Loop through columns and apply filter
  for (question_cols in names(data)) {
    avg <- mean(data[[question_cols]], na.rm = TRUE)
    s <- sd(data[[question_cols]], na.rm = TRUE)
    data <- data[abs(data[[question_cols]] - avg) <= 3 * s, ]
  }
  return(data)
}

### Filter Data with 3 SD

Data_All_Average_Exclusions <- filter_data(Data_All_Average_Pass1[, question_cols])
Data_All_Ideal_Exclusions <- filter_data(Data_All_Ideal_Pass1[, question_cols])
Data_All_Reasonable_Exclusions <- filter_data(Data_All_Reasonable_Pass1[, question_cols])

### Calculate the mean for each column after excluding outlier responses

filtered_column_means_average <- colMeans(Data_All_Average_Exclusions[, question_cols], na.rm = TRUE)

filtered_column_means_reasonable <- colMeans(Data_All_Reasonable_Exclusions[, question_cols], na.rm = TRUE)

filtered_column_means_ideal <- colMeans(Data_All_Ideal_Exclusions[, question_cols], na.rm = TRUE)

```

```{r}

## Step 3: Convert mean responses to a natural log scale.

log_filtered_column_means_average <- log(filtered_column_means_average)

log_filtered_column_means_reasonable <- log(filtered_column_means_reasonable)

log_filtered_column_means_ideal <- log(filtered_column_means_ideal)

print(paste("LogAverages for Averages: ", log_filtered_column_means_average))
print(paste("LogAverages for Reasonable:", log_filtered_column_means_reasonable))
print(paste("LogAverages for Ideal:", log_filtered_column_means_ideal))

```

```{r}

## Step 4: Conduct three regressions: (Model I) one in which average predicts reasonable, (Model II) one in which ideal predicts reasonable, (Model III) one in which both average and ideal predict reasonable judgments. For each regression, record the AIC.

### Make a new DataFrame

dataforAICMeans <- data.frame(Reasonable = log_filtered_column_means_reasonable, Average = log_filtered_column_means_average, Ideal = log_filtered_column_means_ideal)

### Conduct Regressions

#### Model I

Model1Means <- lm(Reasonable ~ Average, data=dataforAICMeans)
AIC1Means <- AIC(Model1Means)

#### Model II

Model2Means <- lm(Reasonable ~ Ideal, data=dataforAICMeans)
AIC2Means <- AIC(Model2Means)

#### Model III

Model3Means <- lm(Reasonable ~ Average + Ideal, data=dataforAICMeans)
AIC3Means <- AIC(Model3Means)

print(paste("AIC for Model 1 - Average predicts Reasonable: ", AIC1Means))
print(paste("AIC for Model 2 - Ideal predicts Reasonable", AIC2Means))
print(paste("AIC for Model 3 - Average and Ideal predict Reasonable", AIC3Means))


```

# Analysis 2: Overall results, intermediacy [following Bear & Knobe 2016]

```{r}

# Step 1: Exclude participants whose answer to Q19 does not equal 15 [comprehension/attention question].

## Previously Calculated in Part 1


# Step 2: For each of the 33 questions (e.g. Q1, Q2, but not Q19) and each of the 3 conditions (reasonable, average, or ideal), compute the mean rating. For any response that is greater than 3 standard deviations from that question mean, exclude that response. 

## Previously Calculated in Part 1


# Step 3: For each question, compute whether the mean reasonableness rating is on the “ideal side” of average. Conduct a binomial test to assess whether the proportion of mean ratings on the “ideal side of the average” is greater than 50%. 

## Determine if reasonableness is on the "ideal side" of average for each question
is_ideal_side <- function(average, ideal, reasonable) {
  ifelse(abs(reasonable - average) > abs(ideal - average), 1, 0)
}

ideal_side_vector <- mapply(is_ideal_side, 
                            filtered_column_means_average, 
                            filtered_column_means_ideal, 
                            filtered_column_means_reasonable)

ideal_side_vector_log <- mapply(is_ideal_side, 
                            log_filtered_column_means_average, 
                            log_filtered_column_means_ideal, 
                            log_filtered_column_means_reasonable)

## Count how many times reasonableness is on the "ideal side" of average
count_ideal_side <- sum(ideal_side_vector)
count_ideal_side_log <- sum(ideal_side_vector_log)

## Conduct a binomial test
binomial_result_ideal <- binom.test(count_ideal_side, length(question_cols), p = 0.5, alternative = "greater")

binomial_result_ideal_log <- binom.test(count_ideal_side_log, length(question_cols), p = 0.5, alternative = "greater")

print(binomial_result_ideal)
print(binomial_result_ideal_log)

# Step 4: For each question, compute whether the mean reasonableness rating is on the “average side” of ideal. Conduct a binomial test to assess whether the proportion of mean ratings on the “average side of the ideal” is greater than 50%. 

## Determine if reasonableness is on the "average side" of ideal for each question
is_average_side <- function(average, ideal, reasonable) {
  ifelse(abs(reasonable - ideal) > abs(average - ideal), 1, 0)
}

average_side_vector <- mapply(is_average_side, 
                              filtered_column_means_average, 
                              filtered_column_means_ideal, 
                              filtered_column_means_reasonable)

average_side_vector_log <- mapply(is_average_side, 
                              log_filtered_column_means_average, 
                              log_filtered_column_means_ideal, 
                              log_filtered_column_means_reasonable)

# Count how many times reasonableness is on the "average side" of ideal
count_average_side <- sum(average_side_vector)
count_average_side_log <- sum(average_side_vector_log)

# Conduct a binomial test
binomial_result_avg_side <- binom.test(count_average_side, length(question_cols), p = 0.5, alternative = "greater")

binomial_result_avg_side_log <- binom.test(count_average_side_log, length(question_cols), p = 0.5, alternative = "greater")

print(binomial_result_avg_side)
print(binomial_result_avg_side_log)

# Step 5: Compute whether the mean reasonableness rating is both on the ideal side of average and average side of ideal, and compute a binomial test to assess whether the distribution differs from chance (with 1/3 as the chance rate).

# Determine if reasonableness is both on the "ideal side" of average and on the "average side" of ideal
is_both_sides <- function(average, ideal, reasonable) {
  ideal_side <- abs(reasonable - average) > abs(ideal - average)
  average_side <- abs(reasonable - ideal) > abs(average - ideal)
  if(ideal_side & average_side) return(1) else return(0)
}

both_sides_vector <- mapply(is_both_sides, 
                            filtered_column_means_average, 
                            filtered_column_means_ideal, 
                            filtered_column_means_reasonable)

both_sides_vector_log <- mapply(is_both_sides, 
                            log_filtered_column_means_average, 
                            log_filtered_column_means_ideal, 
                            log_filtered_column_means_reasonable)

# Count how many times reasonableness is on both sides
count_both_sides <- sum(both_sides_vector)
count_both_sides_log <- sum(both_sides_vector_log)

# Conduct a binomial test with 1/3 as the chance rate
binomial_result_both_sides <- binom.test(count_both_sides, length(question_cols), p = 1/3, alternative = "two.sided")

binomial_result_both_sides_log <- binom.test(count_both_sides_log, length(question_cols), p = 1/3, alternative = "two.sided")

print(binomial_result_both_sides)
print(binomial_result_both_sides_log)

```
# Analysis 3: Overall results, with median ratings 

```{r}

# Step 1: Exclude participants whose answer to Q19 does not equal 15 [comprehension/attention question].

# Completed in Part 1

# Step 2: For each of the 33 questions (e.g. Q1, Q2, but not Q19) and each of the 3 conditions (reasonable, average, or ideal), compute the median rating. 

filter_data_median <- function(data) {
  #### Loop through columns and apply filter
  for (question_cols in names(data)) {
    median <- median(data[[question_cols]], na.rm = TRUE)
  }
  return(data)
}

medians_average_pass <- filter_data_median(Data_All_Average_Pass1[, question_cols])
medians_reasonable_pass <- filter_data_median(Data_All_Reasonable_Pass1[, question_cols])
medians_ideal_pass <- filter_data_median(Data_All_Ideal_Pass1[, question_cols])

medians_average <- apply(medians_average_pass[, question_cols], 2, median, na.rm = TRUE)
medians_reasonable <- apply(medians_reasonable_pass[, question_cols], 2, median, na.rm = TRUE)
medians_ideal <- apply(medians_ideal_pass [, question_cols], 2, median, na.rm = TRUE)

```

```{r}

# Step 3: Convert median responses to a natural log scale

log_medians_average <- log(medians_average)
log_medians_reasonable <- log(medians_reasonable)
log_medians_ideal <- log(medians_ideal)
log_medians_ideal[log_medians_ideal == -Inf] <- 0


```

```{r}

# Step 4: Conduct three regressions: (i) one in which average predicts reasonable, (ii) one in which ideal predicts reasonable, (iii) one in which both average and ideal predict reasonable judgments. For each regression, record the AIC.

### Make a new DataFrame

dataforAICMedians <- data.frame(Reasonable = log_medians_reasonable, Average = log_medians_average, Ideal = log_medians_ideal)

### Conduct Regressions

#### Model I

Model1Medians <- lm(Reasonable ~ Average, data=dataforAICMedians)
AIC1Medians <- AIC(Model1Means)

#### Model II

Model2Medians <- lm(Reasonable ~ Ideal, data=dataforAICMedians)
AIC2Medians <- AIC(Model2Medians)

#### Model III

Model3Medians <- lm(Reasonable ~ Average + Ideal, data=dataforAICMedians)
AIC3Medians <- AIC(Model3Medians)

print(paste("AIC for Model 1 Medians - Average predicts Reasonable: ", AIC1Medians))
print(paste("AIC for Model 2 Medians - Ideal predicts Reasonable", AIC2Medians))
print(paste("AIC for Model 3 Medians - Average and Ideal predict Reasonable", AIC3Medians))

```
# Analysis 4: Overall results, intermediacy, with median ratings 

```{r}

# Determine if median reasonableness is on the "ideal side" of average for each question
is_ideal_side <- function(average, ideal, reasonable) {
  ifelse(abs(reasonable - average) <= abs(ideal - average), 1, 0)
}

ideal_side_vector <- mapply(is_ideal_side, 
                            medians_average, 
                            medians_ideal, 
                            medians_reasonable)

# Count how many times median reasonableness is on the "ideal side" of average
count_ideal_side <- sum(ideal_side_vector)

# Conduct a binomial test
binomial_result_ideal_median <- binom.test(count_ideal_side, length(medians_reasonable), p = 0.5, alternative = "greater")

print(binomial_result_ideal_median)

```

```{r}

# Determine if median reasonableness is on the "average side" of ideal
is_average_side <- function(average, ideal, reasonable) {
  ifelse(abs(reasonable - ideal) <= abs(average - ideal), 1, 0)
}

average_side_vector <- mapply(is_average_side, 
                              medians_average, 
                              medians_ideal, 
                              medians_reasonable)

# Count how many times median reasonableness is on the "average side" of ideal
count_average_side <- sum(average_side_vector)

# Conduct a binomial test
binomial_result_avg_side_medians <- binom.test(count_average_side, length(medians_reasonable), p = 0.5, alternative = "greater")

print(binomial_result_avg_side_medians)

```

```{r}

# Determine if median reasonableness is both on the "ideal side" of average and on the "average side" of ideal
is_both_sides <- function(average, ideal, reasonable) {
  ideal_side <- abs(reasonable - average) <= abs(ideal - average)
  average_side <- abs(reasonable - ideal) <= abs(average - ideal)
  if(ideal_side & average_side) return(1) else return(0)
}

both_sides_vector <- mapply(is_both_sides, 
                            medians_average, 
                            medians_ideal, 
                            medians_reasonable)

# Count how many times median reasonableness is on both sides
count_both_sides <- sum(both_sides_vector)

# Conduct a binomial test with 1/3 as the chance rate
binomial_result_both_sides_medians <- binom.test(count_both_sides, length(medians_reasonable), p = 1/3, alternative = "two.sided")

print(binomial_result_both_sides_medians)

```
# Analysis 5: Overall results, mean ratings [following Bear & Knobe 2016] BY COUNTRY

```{r}

# Split the data by country and store in a list function
split_data_by_country <- function(data) {
  split(data, data$Country_name)
}

# Function to filter data based on 3 SD criterion
filter_data_country <- function(data) {
  data %>%
    group_by(Country_name) %>%
    mutate(across(all_of(question_cols), 
                  ~ifelse(abs(. - mean(., na.rm = TRUE)) <= 3 * sd(., na.rm = TRUE), ., NA), .names = "filtered_{.col}"))
}

# Split by Country

Data_All_Average_by_country <- split_data_by_country(Data_All_Average_Pass1)
Data_All_Ideal_by_country <- split_data_by_country(Data_All_Ideal_Pass1)
Data_All_Reasonable_by_country <- split_data_by_country(Data_All_Reasonable_Pass1)


Data_All_Average_Filtered_by_country <- lapply(Data_All_Average_by_country, filter_data_country)
Data_All_Ideal_Filtered_by_country <- lapply(Data_All_Ideal_by_country, filter_data_country)
Data_All_Reasonable_Filtered_by_country <- lapply(Data_All_Reasonable_by_country, filter_data_country)


# Calculate the mean for each column after excluding outlier responses for each country
calculate_means_by_country <- function(data_list) {
  lapply(data_list, function(data) {
    data %>%
      summarise(across(starts_with("filtered_"), mean, na.rm = TRUE))
  })
}

filtered_column_means_average_by_country <- calculate_means_by_country(Data_All_Average_Filtered_by_country)
filtered_column_means_ideal_by_country <- calculate_means_by_country(Data_All_Ideal_Filtered_by_country)
filtered_column_means_reasonable_by_country <- calculate_means_by_country(Data_All_Reasonable_Filtered_by_country)

```

```{r}

# Convert to Log

log_transform_means <- function(data_list) {
  lapply(data_list, function(data) {
    data %>%
      mutate(across(where(is.numeric), log))  # Apply log only to numeric columns
  })
}

log_filtered_column_means_average_by_country <- log_transform_means(filtered_column_means_average_by_country)
log_filtered_column_means_ideal_by_country <- log_transform_means(filtered_column_means_ideal_by_country)
log_filtered_column_means_reasonable_by_country <- log_transform_means(filtered_column_means_reasonable_by_country)

```

```{r}

# Step 4: Calculate AIC by Country

# Remove the "Country_name" column for each country's data
log_filtered_column_means_average_by_country <- lapply(log_filtered_column_means_average_by_country, function(df) {
  if ("Country_name" %in% colnames(df)) {
    df$Country_name <- NULL
  }
  return(df)
})

log_filtered_column_means_ideal_by_country <- lapply(log_filtered_column_means_ideal_by_country, function(df) {
  if ("Country_name" %in% colnames(df)) {
    df$Country_name <- NULL
  }
  return(df)
})

log_filtered_column_means_reasonable_by_country <- lapply(log_filtered_column_means_reasonable_by_country, function(df) {
  if ("Country_name" %in% colnames(df)) {
    df$Country_name <- NULL
  }
  return(df)
})

# If problematic values are identified, proceed to remove them and run the regression models
calculate_AIC_by_country <- function(average_data, ideal_data, reasonable_data) {
  lapply(names(average_data), function(country_name) {
    data_country <- data.frame(
      avg = unlist(average_data[[country_name]]),
      ideal = unlist(ideal_data[[country_name]]),
      reasonable = unlist(reasonable_data[[country_name]])
    )
  
    # Model I: average predicts reasonable
    model_I <- lm(reasonable ~ avg, data = data_country)
    aic_I <- AIC(model_I)
    
    # Model II: ideal predicts reasonable
    model_II <- lm(reasonable ~ ideal, data = data_country)
    aic_II <- AIC(model_II)
    
    # Model III: both average and ideal predict reasonable
    model_III <- lm(reasonable ~ avg + ideal, data = data_country)
    aic_III <- AIC(model_III)
    
    return(list(AIC_Model_I = aic_I, AIC_Model_II = aic_II, AIC_Model_III = aic_III))
  })
}

AIC_by_country <- calculate_AIC_by_country(log_filtered_column_means_average_by_country, log_filtered_column_means_ideal_by_country, log_filtered_column_means_reasonable_by_country)

names(AIC_by_country) <- names(log_filtered_column_means_average_by_country)

AIC_by_country

```
# Analysis 6: Overall results, intermediacy [following Bear & Knobe 2016] BY COUNTRY

```{r}

# Step 1 and 2 have been completed

# Step 3: For each question, compute whether the mean reasonableness rating is on the “ideal side” of average. Conduct a binomial test to assess whether the proportion of mean ratings on the “ideal side of the average” is greater than 50%. 

# Function to determine if the mean reasonableness rating is on the “ideal side” of average for each question
is_ideal_side <- function(average, ideal, reasonable) {
  ifelse(abs(reasonable - average) > abs(ideal - average), 1, 0)
}

# Apply the function for each country
ideal_side_results_by_country <- lapply(names(log_filtered_column_means_average_by_country), function(country_name) {
  avg_data <- log_filtered_column_means_average_by_country[[country_name]]
  ideal_data <- log_filtered_column_means_ideal_by_country[[country_name]]
  reasonable_data <- log_filtered_column_means_reasonable_by_country[[country_name]]
  
  mapply(is_ideal_side, avg_data, ideal_data, reasonable_data)
})

# Conduct a binomial test for each country
binomial_test_ideal_side_by_country <- lapply(ideal_side_results_by_country, function(results) {
  sum_results <- sum(results)
  binom.test(sum_results, length(results), p = 0.5)
})

# Assign country names to each list element in binomial_test_results_by_country
names(binomial_test_ideal_side_by_country) <- names(log_filtered_column_means_average_by_country)

# View the binomial test results by country
binomial_test_ideal_side_results_by_country


```

```{r}

# Step 4: For each question, compute whether the mean reasonableness rating is on the “average side” of ideal. Conduct a binomial test to assess whether the proportion of mean ratings on the “average side of the ideal” is greater than 50%. 

# Function to determine if the mean reasonableness rating is on the “average side” of ideal for each question
is_average_side <- function(average, ideal, reasonable) {
  ifelse(abs(reasonable - ideal) > abs(average - ideal), 1, 0)
}

# Apply the function for each country
avg_side_results_by_country <- lapply(names(log_filtered_column_means_average_by_country), function(country_name) {
  avg_data <- log_filtered_column_means_average_by_country[[country_name]]
  ideal_data <- log_filtered_column_means_ideal_by_country[[country_name]]
  reasonable_data <- log_filtered_column_means_reasonable_by_country[[country_name]]
  
  mapply(is_average_side, avg_data, ideal_data, reasonable_data)
})

# Conduct a binomial test for each country
binomial_test_avg_side_by_country <- lapply(avg_side_results_by_country, function(results) {
  sum_results <- sum(results)
  binom.test(sum_results, length(results), p = 0.5)
})

# Assign country names to each list element in binomial_test_avg_side_by_country
names(binomial_test_avg_side_by_country) <- names(log_filtered_column_means_average_by_country)

# View the binomial test results by country for average side of ideal
binomial_test_avg_side_by_country

```



```{r}

# Step 5: For each question, compute whether the mean reasonableness rating is both on the ideal side of average and average side of ideal, and compute a binomial test to assess whether the distribution differs from chance (with 1/3 as the chance rate).

# Function to determine if the mean reasonableness rating is on both sides

is_both_sides <- function(average, ideal, reasonable) {
  ideal_side <- abs(reasonable - average) > abs(ideal - average)
  average_side <- abs(reasonable - ideal) > abs(average - ideal)
  if(ideal_side & average_side) return(1) else return(0)
}

# Apply the function for each country
both_sides_results_by_country <- lapply(names(log_filtered_column_means_average_by_country), function(country_name) {
  avg_data <- log_filtered_column_means_average_by_country[[country_name]]
  ideal_data <- log_filtered_column_means_ideal_by_country[[country_name]]
  reasonable_data <- log_filtered_column_means_reasonable_by_country[[country_name]]
  
  mapply(is_both_sides, avg_data, ideal_data, reasonable_data)
})

# Conduct a binomial test for each country with 1/3 as the chance rate
binomial_test_both_sides_by_country <- lapply(both_sides_results_by_country, function(results) {
  sum_results <- sum(results)
  binom.test(sum_results, length(results), p = 1/3)
})

names(binomial_test_both_sides_by_country) <- names(log_filtered_column_means_average_by_country)

binomial_test_both_sides_by_country

```

# Analysis 7: Overall results, with median ratings BY COUNTRY

```{r}

# Function to compute median for each question by country
compute_median_by_country <- function(data_list) {
  lapply(data_list, function(data) {
    data %>%
      group_by(Country_name) %>%
      summarise(across(all_of(question_cols), median, na.rm = TRUE))
  })
}

# Apply the function to each condition
median_ratings_average_by_country <- compute_median_by_country(Data_All_Average_by_country)
median_ratings_ideal_by_country <- compute_median_by_country(Data_All_Ideal_by_country)
median_ratings_reasonable_by_country <- compute_median_by_country(Data_All_Reasonable_by_country)


```


```{r}

# Function to convert median ratings to natural log scale
convert_to_log_scale <- function(data_list) {
  lapply(data_list, function(data) {
    data %>%
      mutate(across(all_of(question_cols), log))
  })
}

# Apply the function to each condition's median ratings
log_median_ratings_average_by_country <- convert_to_log_scale(median_ratings_average_by_country)
log_median_ratings_ideal_by_country <- convert_to_log_scale(median_ratings_ideal_by_country)
log_median_ratings_reasonable_by_country <- convert_to_log_scale(median_ratings_reasonable_by_country)

# Function to replace -Inf values with 0
replace_minus_inf_with_zero <- function(data_list) {
  lapply(data_list, function(data) {
    data %>%
      mutate(across(everything(), ~replace(., is.infinite(.) & . < 0, 0)))
  })
}

# Apply the function to each dataset
log_median_ratings_average_by_country <- replace_minus_inf_with_zero(log_median_ratings_average_by_country)
log_median_ratings_ideal_by_country <- replace_minus_inf_with_zero(log_median_ratings_ideal_by_country)
log_median_ratings_reasonable_by_country <- replace_minus_inf_with_zero(log_median_ratings_reasonable_by_country)

```


```{r}

# Step 4: Calculate AIC by Country

# Remove the "Country_name" column for each country's data
log_median_ratings_average_by_country <- lapply(log_median_ratings_average_by_country, function(df) {
  if ("Country_name" %in% colnames(df)) {
    df$Country_name <- NULL
  }
  return(df)
})

log_median_ratings_ideal_by_country <- lapply(log_median_ratings_ideal_by_country, function(df) {
  if ("Country_name" %in% colnames(df)) {
    df$Country_name <- NULL
  }
  return(df)
})

log_median_ratings_reasonable_by_country <- lapply(log_median_ratings_reasonable_by_country, function(df) {
  if ("Country_name" %in% colnames(df)) {
    df$Country_name <- NULL
  }
  return(df)
})

# Calculate AIC by Country Function

calculate_AIC_by_country <- function(average_data, ideal_data, reasonable_data) {
  lapply(names(average_data), function(country_name) {
    data_country <- data.frame(
      avg = unlist(average_data[[country_name]]),
      ideal = unlist(ideal_data[[country_name]]),
      reasonable = unlist(reasonable_data[[country_name]])
    )
  
    # Model I: average predicts reasonable
    model_I <- lm(reasonable ~ avg, data = data_country)
    aic_I <- AIC(model_I)
    
    # Model II: ideal predicts reasonable
    model_II <- lm(reasonable ~ ideal, data = data_country)
    aic_II <- AIC(model_II)
    
    # Model III: both average and ideal predict reasonable
    model_III <- lm(reasonable ~ avg + ideal, data = data_country)
    aic_III <- AIC(model_III)
    
    return(list(AIC_Model_I = aic_I, AIC_Model_II = aic_II, AIC_Model_III = aic_III))
  })
}

AIC_by_country_medians <- calculate_AIC_by_country(log_median_ratings_average_by_country, log_median_ratings_ideal_by_country, log_median_ratings_reasonable_by_country)

names(AIC_by_country_medians) <- names(log_filtered_column_means_average_by_country)

AIC_by_country_medians

```
# Analysis 8: Overall results, intermediacy, with median ratings BY COUNTRY

```{r}

# Step 1 and 2 have been completed

# Step 3: For each question, compute whether the mean reasonableness rating is on the “ideal side” of average. Conduct a binomial test to assess whether the proportion of mean ratings on the “ideal side of the average” is greater than 50%. 

# Function to determine if the mean reasonableness rating is on the “ideal side” of average for each question
is_ideal_side <- function(average, ideal, reasonable) {
  ifelse(abs(reasonable - average) > abs(ideal - average), 1, 0)
}

# Apply the function for each country
ideal_side_results_by_country <- lapply(names(log_filtered_column_means_average_by_country), function(country_name) {
  avg_data <- log_median_ratings_average_by_country[[country_name]]
  ideal_data <- log_median_ratings_ideal_by_country[[country_name]]
  reasonable_data <- log_median_ratings_reasonable_by_country[[country_name]]
  
  mapply(is_ideal_side, avg_data, ideal_data, reasonable_data)
})

# Conduct a binomial test for each country
binomial_median_test_ideal_side_results_by_country <- lapply(ideal_side_results_by_country, function(results) {
  sum_results <- sum(results)
  binom.test(sum_results, length(results), p = 0.5)
})

# Assign country names to each list element in binomial_test_results_by_country
names(binomial_median_test_ideal_side_results_by_country) <- names(log_median_ratings_average_by_country)

# View the binomial test results by country
binomial_median_test_ideal_side_results_by_country


```

```{r}

# Step 4: For each question, compute whether the mean reasonableness rating is on the “average side” of ideal. Conduct a binomial test to assess whether the proportion of mean ratings on the “average side of the ideal” is greater than 50%. 

# Function to determine if the mean reasonableness rating is on the “average side” of ideal for each question
is_average_side <- function(average, ideal, reasonable) {
  ifelse(abs(reasonable - ideal) > abs(average - ideal), 1, 0)
}

# Apply the function for each country
avg_side_results_by_country <- lapply(names(log_filtered_column_means_average_by_country), function(country_name) {
  avg_data <- log_median_ratings_average_by_country[[country_name]]
  ideal_data <- log_median_ratings_ideal_by_country[[country_name]]
  reasonable_data <- log_median_ratings_reasonable_by_country[[country_name]]
  
  mapply(is_average_side, avg_data, ideal_data, reasonable_data)
})

# Conduct a binomial test for each country
binomial_test_avg_side_by_country_median <- lapply(avg_side_results_by_country, function(results) {
  sum_results <- sum(results)
  binom.test(sum_results, length(results), p = 0.5)
})

# Assign country names to each list element in binomial_test_avg_side_by_country
names(binomial_test_avg_side_by_country_median) <- names(log_filtered_column_means_average_by_country)

# View the binomial test results by country for average side of ideal
binomial_test_avg_side_by_country_median
```

```{r}

# Step 5: For each question, compute whether the mean reasonableness rating is both on the ideal side of average and average side of ideal, and compute a binomial test to assess whether the distribution differs from chance (with 1/3 as the chance rate).

# Function to determine if the mean reasonableness rating is on both sides

is_both_sides <- function(average, ideal, reasonable) {
  ideal_side <- abs(reasonable - average) > abs(ideal - average)
  average_side <- abs(reasonable - ideal) > abs(average - ideal)
  if(ideal_side & average_side) return(1) else return(0)
}

# Apply the function for each country
both_sides_results_by_country <- lapply(names(log_filtered_column_means_average_by_country), function(country_name) {
  avg_data <- log_median_ratings_average_by_country[[country_name]]
  ideal_data <- log_median_ratings_ideal_by_country[[country_name]]
  reasonable_data <- log_median_ratings_reasonable_by_country[[country_name]]
  
  mapply(is_both_sides, avg_data, ideal_data, reasonable_data)
})

# Conduct a binomial test for each country with 1/3 as the chance rate
binomial_test_both_sides_by_country_median <- lapply(both_sides_results_by_country, function(results) {
  sum_results <- sum(results)
  binom.test(sum_results, length(results), p = 1/3)
})

names(binomial_test_both_sides_by_country_median) <- names(log_filtered_column_means_average_by_country)

binomial_test_both_sides_by_country_median

```

